Stochastic Variance Reduced Policy Gradient

### 2018-02-04 svrpg.tex
Updated

To deal with non-convexity, we require $J(\vtheta)$ to be $L$-smooth, which is a reasonable assumption for common policy classes such as truncated Gaussian and softmax (see App.~\ref{app:lsmoothness}.\todopirout{search for ref}
Because of the infinite dataset, we can only rely on an estimate of the full gradient. 

>>>>

To deal with non-convexity, we require $J(\vtheta)$ to be $L$-smooth, which is a reasonable assumption for common policy classes such as truncated Gaussian and softmax (see App.~\ref{app:lsmoothness}).\todopirout{search for ref}
Because of the infinite dataset, we can only rely on an estimate of the full gradient. \citet{harikandeh2015stopwasting} analyzed this scenario under concavity \textcolor{red}{assumptions} of $g$, showing that SVRG is robust to inexact computation of the full gradient. In particular, it is still possible to recover the original convergence rate is the error decreases at an appropriate rate. {\color{red}Later on we will show how the estimation accuracy impacts on the convergence results with smooth objective.} 
